### 2018-04-19 papers/synth/abstract.tex
ASd

Vesicle Traffic Systems are the transport mechanisms inside the cells.
%
Different compartments are viewed as nodes and transport channels are
nodes between the graphs.

>>>>

Vesicle Traffic Systems(VTS) are the material transport mechanisms
among the compartments inside the biological cells.
%
The compartments are viewed as nodes that are labeled with the containing
chemicals and the transport channels are labeled edges between the
nodes.
%
Understanding VTSs is an ongoing area of research and for many cells
they are partially known.
%
For examples, there may be undiscovered edges, nodes, or their labels
in a VTS of a cell.
%
It has been speculated that there are properties that the VTSs must satisfy.
%
For example stability, i.e., every chemical that is leaving a compartment comes back.
%
Many synthesis questions may arise in this scenario, where we want
to complete a partially known VTS under a given property.
%
In the paper, we present novel encodings of the above questions
into the QBF satisfiability problems.
%
We have implemented the encodings in a highly configurable tool
and  apply to a couple of found-in-nature VTSs and 
several synthetic graphs.
%
Our results demonstrates that our method can scale upto the
graphs of interest.
%
